---
title: "Gun Control Chi-Square"
author: "Jeremy Knox"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Sup Superbad. 

<<<<<<< HEAD

Hallo friends
this is line 18
=======
upadte yo.

<<<<<<< HEAD
editing line 18. jknox 



```{r}
library(tidyverse)
gc_df <- read_csv("gc_df.csv")


get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA")  %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female", "Male")


```


I'm the collaborator (Nakoa) and I am going to chi-square test for the gun control data

Phrasing the question (multiple ways)
Is there a significant difference in gun control perspectives (as related to access to guns) for males and females?

Is there a significant association between sex and gun control recommendations?

Is perception of gun control access independent of sex?

Chi-Square
```{r}
# create a table of proportions by row (based on responses by gender) . prop.table wants to work with a matrix data structure, not a tible
guns_prop <- prop.table(as.matrix(get_guns), 1) # only calculate proportions across rows

guns_prop

# Performing chi-square (very easy with contingency table set up like get_guns)

guns_x2 <- chisq.test(get_guns)
guns_x2

# H0: sex is independent of gun access preference

```
Recommended gov. action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`) = ...., p < 0.001, $\alpha$ = 0.05). Fifty-seven percent of females responded that access to guns should be more difficult, which 40 percent of male respondents agreed with. 

